A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-15 draft.tex
Update SOA

Although at first sight containers look like simply a method that
allows easy shipping of applications, they are much more than
that. One of the first features that make them interesting is their
ephemerality: fast startup and teardown time make them usable for
machine-independent and cloud deployment of simple, ephemeral and
maybe stateless functions. On the other hand, containerization also
allows, through the use of orchestration engines like Docker Swarm or
Kubernetes, or through simple, non-self-scaling specifications using
{\tt docker-compose}, a definition of all the relationships between
different parts of the application, or services. The full realization
of Docker-based architectures has led to the creation of a series of
patterns that, together, conform cloud-native application development
\cite{kratzke2017understanding}.

However, in the field of evolutionary algorithms, this has been a slow
realization, from the origins where Salza and Ferrucci
\cite{salza2016approach,salza2016develop} proposed an architecture that carried
evolutionary algorithms to the cloud, and which were developed further in their
next paper \cite{de2017parallel}. These papers started to introduce cloud native
aspects such as the use of messaging queues and CoreOS as an operating system
designed from the ground up for container utilization in the area of
evolutionary algorithms. The way these containers are managed, however, is
rather classical in nature from the point of view of distributed EC: a
master-worker approach, communicated using RabbitMQ (a messaging queue), where
replicated workers perform the tasks in parallel. They called their approach
AMQPGA, inspired by the protocol, AMQP, used by RabbitMQ, the messaging system.
Other authors have also followed this classical approach by using other EA
``classical'' topologies in the cloud: Dziurzanski et al.
\cite{dziurzanski2020scalable} adapts an island model to a container
architecture, in a system that is functionally equivalent to classical models,
with the advantage of the auto-scaling of islands, and being easy to deploy and
run.

Later approaches use microservices \cite{khalloof2018generic}, or were
systematized \cite{salza2019speed} achieving speed-up through the
creation of an abstraction layer over the evolutionary algorithm
services, and also automation of the whole workflow. This research
bumped into some problems, since speed-up is limited, mainly due to the
non-automatic scaling of services and also the presence of a single
master which is the one that runs the evolutionary
algorithms. However, this master-worker architecture can be turned
around with other kind of evolutionary architectures, such
as pool-based systems
\cite{valenzuela2015implementing,merelo2012sofea,sofea:cec2012} where
a better match to the inherently heterogeneous nature of cloud-based
architectures. Pool-based systems are closer to serverless systems
\cite{malawski2017serverless}, and they pull from the pool and run
whole algorithms, instead of just evaluation. The pool from where they
pull is the common store of results, and can be accessed in an
asynchronous way, which suits better the nature of cloud systems.

>>>>

Although containers look like merely a method for easy shipping 
of applications, at first sight, they are much more than
that. One of the first features that make them interesting is their
ephemerality: fast startup and teardown time make them usable for
machine-independent and cloud deployment of simple, ephemeral, and
maybe stateless functions. 
%On the other hand, containerization also
%allows, through the use of orchestration engines like Docker Swarm or
%Kubernetes, or through simple, non-self-scaling specifications using
%{\tt docker-compose}, a definition of all the relationships between
%different parts of the application, or services. 
% We said this earlier - Mario
The full realization
of Docker-based architectures has led to the creation of a series of
patterns that together define the cloud-native application development
\cite{kratzke2017understanding}.

However, this has been a slow realization in the evolutionary algorithms 
field, from the origins where Salza and Ferrucci \cite{salza2016approach,salza2016develop} 
proposed an architecture that carried evolutionary algorithms to the cloud, 
and which were developed further in their next paper \cite{de2017parallel}.
These papers started to introduce cloud-native
aspects such as the use of messaging queues and CoreOS as an operating system
designed from the ground up for container utilization in the area of
evolutionary algorithms. However, the way these containers are managed, is
rather classical from the distributed EC point of view: a
master-worker approach, communicated using RabbitMQ (a messaging queue), where
replicated workers perform the tasks in parallel. They called their approach
AMQPGA, inspired by the protocol, AMQP, used by RabbitMQ.
Other authors have also followed this classical approach by using other 
``classical'' EA topologies in the cloud: Dziurzanski et al.
\cite{dziurzanski2020scalable} adapts an island model to a container
architecture, in a system that is functionally equivalent to classical models,
with the advantage of the auto-scaling of islands, and being easy to deploy and
run.

Later approaches used microservices \cite{khalloof2018generic} and 
provided the automation of the whole workflow\cite{salza2019speed}, 
achieving speed-up by creating an abstraction layer over the 
evolutionary algorithm services.
%, and also automation of the whole workflow. 
This research bumped into some problems, since speed-up is limited, mainly due to the
non-automatic scaling of services and the presence of a single
master, which is the one that runs the evolutionary
algorithm. However, this master-worker architecture can be turned
around with other kinds of evolutionary architectures, such
as pool-based systems
\cite{valenzuela2015implementing,merelo2012sofea,sofea:cec2012} that were 
a better match to the inherently heterogeneous nature of cloud-based
architectures. Pool-based systems are closer to serverless systems
\cite{malawski2017serverless}, as they pull populations from the pool and run
whole algorithms, instead of just doing the evaluation. The pool 
is a shared data storage for results, and can be accessed in an
asynchronous way, which suits better the nature of cloud-native systems.
